### 2012-10-02 inst/examples/Reed.Rmd

``` {r }
xmin <- 0
xmax <- K
grid_n <- 200
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .2
````

@@

``` {r noise}
#z_g <- function() 1 + rlnorm(1,0, sigma_g)  
z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
````

``` {r  SDP_Mat}
pdfn <- function(P, s){
   dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````

>>>>

``` {r }
xmin <- 0
xmax <- K*1.5
grid_n <- 200
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .1
````

@@

``` {r noise}
z_g <- function() 1 + rlnorm(1,0, sigma_g)  
pdfn <- function(P, s) dlnorm(P, 0, s)

#z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
#pdfn <- function(P, s)  dunif(P, 1 - s, 1 + s)
````

``` {r  SDP_Mat}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````
